Ceph Parallel File System Evaluation Report

### 2013-11-07 baseline.tex
shrink Section 3 and 4.1 to fit 5 pages

The lowest layer in the system are the exposed LUNs to the server hosts from
the RAID controllers.  These LUNs are configured as a RAID 6 8+2 array (8 data
disks and 2 \textit{P} and \textit{Q} disks). In prior tests we observed
that a 7.2K RPM SAS disk can perform at 140 MB/s for 128 kB
sequential I/O requests and a 7.2K RPM SATA disk can do 36 MB/s.
For these tests, all disk caches were turned off. Therefore, in 8 data disk
RAID group with 1 MB sequential I/O requests (each disks sees 128 kB chunks of
the request) the aggregate performance is about 1.12
GB/s for a SAS RAID group and 288 MB/s for a SATA RAID group, if
there are no caches along the I/O path.  With the caches turned on, especially
the write-back cache on the DDN RAID controller, we observe a significant
performance improvement. In our day-to-day HPC operations we run our storage
systems with write-back cache turned on on RAID controllers, if and only if,
there is a method of cache-mirroring between the two active-active RAID
controllers. With the write-back cache on we observe \textasciitilde1.4 GB/s
per RAID 6 8+2 SAS group and  \textasciitilde955 MB/s per RAID 6 8+2 SATA
group, for 1 MB sequential I/O.  These two performance numbers will be used as
a baseline in our study and they are presented in
Table~\ref{tbl:block-io-baseline}.  For these tests, the 8+2 RAID 6 groups are
exported to the server hosts using SCSI RDMA Protocol (SRP) over IB protocol
(which is the default for our normal HPC configurations). For a SATA disk group
this translates into roughly 120 MB/s/disk and for a SAS disk group it is 175
MB/s/disk. As can be seen, SATA RAID groups benefit from caching more than SAS
groups.

>>>>

The lowest layer in the system are the exposed LUNs to the server hosts from
the RAID controllers.  These LUNs are configured as a RAID 6 8+2 array (8 data
disks and 2 \textit{P} and \textit{Q} disks).

%In prior tests we observed
%that a 7.2K RPM SAS disk can perform at 140 MB/s for 128 kB
%sequential I/O requests and a 7.2K RPM SATA disk can do 36 MB/s.
%For these tests, all disk caches were turned off. Therefore, in 8 data disk
%RAID group with 1 MB sequential I/O requests (each disks sees 128 kB chunks of
%the request) the aggregate performance is about 1.12
%GB/s for a SAS RAID group and 288 MB/s for a SATA RAID group, if
%there are no caches along the I/O path.  With the caches turned on, especially
%the write-back cache on the DDN RAID controller, we observe a significant
%performance improvement.

In our day-to-day HPC operations, we run our storage
systems with write-back cache turned on on RAID controllers, if and only if,
there is a method of cache-mirroring between the two active-active RAID
controllers. With the write-back cache on we observe \string~1.4 GB/s
per RAID 6 8+2 SAS group and  \string~955 MB/s per RAID 6 8+2 SATA
group, for 1 MB sequential I/O.  These two performance numbers will be used as
a baseline in our study and they are presented in
Table~\ref{tbl:block-io-baseline}.  For these tests, the 8+2 RAID 6 groups are
exported to the server hosts using SCSI RDMA Protocol (SRP) over IB protocol
(which is the default for our normal HPC configurations). For a SATA disk group
this translates into roughly 120 MB/s/disk and for a SAS disk group it is 175
MB/s/disk. As can be seen, SATA RAID groups benefit from caching more than SAS
groups.

### 2013-11-07 testbed.tex
shrink Section 3 and 4.1 to fit 5 pages

Our SFA10K system consists of 200 SAS drives and 280 SATA drives, hosted in a
10-tray configuration. Each DDN SA4601 disk tray can host up to 60 disks and
has two SAS links per controller (four in total). The SATA and SAS disks in our
testbed are distributed evenly over ten SA4601 disk trays (20 SAS and 28 SATA
disks per tray). Each SFA10K RAID controller has two RAID processors and each
RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
groups by the RAID processors (software RAID) and then exported to connected
server hosts over the IB connections. Since each DDN SFA10K controller is a
stand-alone computer system running Linux, CPU and memory affinity while
organizing disks into RAID groups and exporting them is crucial for obtaining
top performance out of an SFA10K system.

>>>>

Our SFA10K system consists of 200 SAS drives and 280 SATA drives, hosted in a
10-tray configuration.
%Each DDN SA4601 disk tray can host up to 60 disks and
%has two SAS links per controller (four in total). The SATA and SAS disks in our
%testbed are distributed evenly over ten SA4601 disk trays (20 SAS and 28 SATA
%disks per tray). 
%Each SFA10K RAID controller has two RAID processors and each
%RAID processor hosts a dual-port IB QDR card. The disks are organized into RAID
%groups by the RAID processors (software RAID) and then exported to connected
%server hosts over the IB connections. 
Since each DDN SFA10K controller is a
stand-alone computer system running Linux, CPU and memory affinity while
organizing disks into RAID groups and exporting them is crucial for obtaining
top performance out of an SFA10K system.
